Enhancement of SDR in Thessaloniki

### 2024-01-18 GHI_enh_04_investigate.tex
Commit 2024-01-18 18:18

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-17}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Loading required package: stringr
\end{verbatim}

\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

\hypertarget{trends-daily}{%
\subsubsection{Trends daily}\label{trends-daily}}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\begin{verbatim}
2024-01-17 10:06:09.7 athan@sagan GHI_enh_04_investigate.R 0.091749 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-18}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

\hypertarget{daily-trends}{%
\subsubsection{Daily Trends}\label{daily-trends}}

@@

\begin{verbatim}
Loading required package: stringr
\end{verbatim}

@@

lmD: 1.71458 +/- 0.1322584

lmY: 1.714601 +/- 0.1322612

Tourpali: 1.7152 0.1817 9.4404 0

@@

lmD: 1.015311 +/- 0.173386

lmY: 1.015342 +/- 0.1733898

Tourpali: 1.1004 0.255 4.3146 0

lmD: -0.1672102 +/- 0.1436958

lmY: -0.1672003 +/- 0.1436989

\begin{verbatim}
Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
possible convergence problem: optim gave code = 1
\end{verbatim}

\begin{verbatim}
Warning in sqrt(diag(se)): NaNs produced

Warning in sqrt(diag(se)): NaNs produced
\end{verbatim}

@@

Tourpali: -0.1679 3.8757 -0.0433 0.9654

@@

lmD: 605.1187 +/- 96.27827

lmY: 605.1308 +/- 96.28033

Tourpali: 605.7835 145.2351 4.1711 0

@@

lmD: 0.002984713 +/- 0.0002850018

lmY: 0.00298475 +/- 0.0002850079

Tourpali: 0.003 4e-04 7.7371 0

@@

lmD: 0.001565283 +/- 0.0003220401

lmY: 0.001565348 +/- 0.000322047

Tourpali: 0.0018 5e-04 3.3956 7e-04

lmD: -0.1672102 +/- 0.1436958

lmY: -0.1672003 +/- 0.1436989

\begin{verbatim}
Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
possible convergence problem: optim gave code = 1

Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
NaNs produced

Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
NaNs produced
\end{verbatim}

@@

lmD: 0.9735636 +/- 0.1446246

lmY: 0.9735884 +/- 0.1446277

Tourpali: 1.0386 0.2143 4.8455 0

@@

lmD: 0.7131394 +/- 0.1236589

lmY: 0.7131522 +/- 0.1236614

Tourpali: 0.7132 0.1476 4.8325 0

@@

lmD: 0.1205603 +/- 0.04472432

lmY: 0.1205635 +/- 0.04472525

Tourpali: 0.1206 0.0487 2.4752 0.0133

@@

lmD: 0.5126011 +/- 0.05584138

lmY: 0.5126089 +/- 0.05584254

Tourpali: 0.5126 0.0703 7.2901 0

@@

lmD: 28.03241 +/- 3.452126

lmY: 28.0328 +/- 3.452198

Tourpali: 28.0362 4.3653 6.4225 0

@@

lmD: 0.001091243 +/- 0.0001452364

lmY: 0.001091258 +/- 0.0001452394

Tourpali: 0.0011 2e-04 6.6404 0

@@

lmD: 0.0002586606 +/- 6.142941e-05

lmY: 0.0002586644 +/- 6.143069e-05

Tourpali: 3e-04 1e-04 3.7461 2e-04

@@

lmD: 0.03561979 +/- 0.004001997

lmY: 0.03562032 +/- 0.004002081

Tourpali: 0.0356 0.0048 7.3697 0

@@

lmD: -0.1184401 +/- 0.3426654

lmY: -0.1183983 +/- 0.3426728

Tourpali: -0.1021 0.5303 -0.1925 0.8473

@@

lmD: -0.2498159 +/- 0.2873017

lmY: -0.2497925 +/- 0.287308

Tourpali: -0.249 0.4778 -0.5212 0.6022

@@

lmD: 0.02397815 +/- 0.02221734

lmY: 0.02397998 +/- 0.02221782

Tourpali: 0.024 0.0229 1.0454 0.2959

@@

lmD: 4.678815 +/- 4.938622

lmY: 4.679265 +/- 4.938728

Tourpali: 4.6804 5.0982 0.9181 0.3586

@@

lmD: 0.0002750923 +/- 0.0002421161

lmY: 0.0002751196 +/- 0.0002421213

Tourpali: 3e-04 3e-04 1.0722 0.2836

@@

lmD: 0.0001464247 +/- 0.0001495252

lmY: 0.0001464348 +/- 0.0001495284

Tourpali: 1e-04 2e-04 0.8844 0.3765

@@

lmD: 0.007036274 +/- 0.006116865

lmY: 0.007036819 +/- 0.006116997

Tourpali: 0.007 0.0063 1.1208 0.2624

@@

\begin{verbatim}
2024-01-18 15:45:20.0 athan@sagan GHI_enh_04_investigate.R 0.179315 mins
\end{verbatim}
